Exponential Integrators for PDEs arising in meteorology

### 2024-09-11 article_4.tex
Added Graphs to Report

\begin{figure}[H]
    \centering
    \begin{minipage}{0.5\textwidth}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v E Results for N=131072.png}
	  \label{fig:MEe7}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v Comp Time Results for N=131072.png}
	  \label{fig:MEe7}
       \centering
	  \includegraphics[width=\linewidth]{Plots/Comp Time v E Results for N=131072.png}
	  \label{fig:MEe7}
    \end{minipage}\hfill
    \begin{minipage}{0.5\textwidth}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v E Results for N=524288.png}
	  \label{fig:MEe6}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v Comp Time Results for N=524288.png}
	  \label{fig:MEe6}
       \centering
	  \includegraphics[width=\linewidth]{Plots/Compt time v E Results for N=524288.png}
	  \label{fig:MEe6}
    \end{minipage}
\end{figure}
These results show that the Lanzcos algorithm outperforms the Arnoldi algorithm in both convergence rate and computational time.

Below we compare the time required for the different algorithms to get below an error of $10^{10}$ when computing $e^Av$ for various matrix sizes.
\begin{figure}[H]
\includegraphics[width=\linewidth]{Plots/time to get below an error of 1e-10.png}
\end{figure}
Again we continue to see that the Lanzcos algorithm outperforms the Arnodli algorithm.
\clearpage
\newpage
\bibliographystyle{plain}
\bibliography{References.bib}

>>>>

\begin{figure}[H]
    \centering
    \begin{minipage}{0.5\textwidth}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v E Results for N=131072.png}
	  \label{fig:MEe7}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v Comp Time Results for N=131072.png}
	  \label{fig:MEe7}
       \centering
	  \includegraphics[width=\linewidth]{Plots/Comp Time v E Results for N=131072.png}
	  \label{fig:MEe7}
    \end{minipage}\hfill
    \begin{minipage}{0.5\textwidth}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v E Results for N=524288.png}
	  \label{fig:MEe6}
       \centering
	  \includegraphics[width=\linewidth]{Plots/M v Comp Time Results for N=524288.png}
	  \label{fig:MEe6}
       \centering
	  \includegraphics[width=\linewidth]{Plots/Comp time v E Results for N=524288.png}
	  \label{fig:MEe6}
    \end{minipage}
\end{figure}
These results show that the Lanzcos algorithm outperforms the Arnoldi algorithm in both convergence rate and computational time.

Below we compare the time required for the different algorithms to get below an error of $10^6$ and $10^{10}$ when computing $e^Av$ for various matrix sizes.
\begin{figure}[H]
\includegraphics[width=\linewidth]{Plots/time to get below an error of 1e-06.png}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\linewidth]{Plots/time to get below an error of 1e-10.png}
\end{figure}
Again we continue to see that the Lanzcos algorithm outperforms the Arnodli algorithm.
\clearpage
\newpage
\bibliographystyle{plain}
\bibliography{References.bib}
